---
title: "QMM - Module 11"
author: "SAMIKSHA VENUGOPAL"
date: "11/20/2022"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r}
library(lpSolveAPI)
library(lpSolve)
```

```{r}

f.obj <- c(775,800,800,800,800,775,750)
f.con <- matrix(c(0,1,1,1,1,1,0,0,0,1,1,1,1,1,1,0,0,1,1,1,1,1,1,0,0,1,1,1,1,1,1,0,0,1,1,1,1,1,1,0,0,1,1,1,1,1,1,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,1),nrow = 14,byrow = TRUE)
f.dir <- c(">=",">=",">=",">=",">=",">=",">=",">=",">=",">=",">=",">=",">=",">=")
f.rhs <- c(18,27,22,26,25,21,19,1,1,1,1,1,1,1)
model <- lp('min',f.obj,f.con,f.dir,f.rhs,int.vec = 1:15)
model
model$solution
```

## Conclusion

We can conclude that minimum cost is 25675



```{r}
### ALternative method

```
           ### ALternative method 
           
   ### Objective Function

775x1 + 800x2 + 800x3 + 800x4 + 800x5 + 775x6 + 750x7 = MINIMIZE        

 Shift 1
 Shift 2 
 Shift 3 
 Shift 4 
 Shift 5 
 Shift 6 
 Shift 7 
 
 # Constraints
 
 (refer)
 
           
```{r}

predict <- make.lp(0, 7)

set.objfn(predict, c(775, 800, 800, 800, 800, 775, 750))

lp.control(predict)

add.constraint(predict, c(0,1,1,1,1,1,0), ">=", 18)
add.constraint(predict, c(0,0,1,1,1,1,1), ">=", 27)
add.constraint(predict, c(1,0,0,1,1,1,1), ">=", 22)
add.constraint(predict, c(1,1,0,0,1,1,1), ">=", 26)
add.constraint(predict, c(1,1,1,0,0,1,1), ">=", 25)
add.constraint(predict, c(1,1,1,1,0,0,1), ">=", 21)
add.constraint(predict, c(1,1,1,1,1,0,0), ">=", 19)



solve(predict)
get.objective(predict)
get.variables(predict)

```
```{r}

    ### ALternative method 

Working_days = matrix(c("Sunday","Monday","Tuesday","Wednesday","Thursay","Friday","Saturday",18,27,22,26,25,21,19),ncol = 2,byrow = F)
colnames(Working_days) =c("Daysoftheweek","Workers")
as.table(Working_days)

```

# interpreration 
x1= 2 working shift 1
x2 = 4  working shift 2
x3 = 5 working shift 3
x4 = 0 working shift 4 
x5 = 8 working shift 5
x6 = 1 working shift 6
x7 = 13 working shift 7


```{r}
consider =  matrix(c(0,4,5,0,8,1,0,0,0,5,0,8,1,13,2,0,0,0,8,1,13,2,4,0,0,8,1,13,2,4,5,0,0,1,13,2,3,4,0,0,0,13,2,4,5,0,8,0,0),ncol=7,byrow=TRUE)
colnames(consider) =c("Shift_1", "Shift_2", "Shift_3", "Shift_4", "Shift_5", "Shift_6", "Shift_7")
row.names(consider) = c('Sunday', 'Monday', 'Tuesday','Wednesday','Thursday','Friday','Saturday')
consider

## no of employees available on daily basic 
rowSums(consider)
```


## Conclusion

Firstly we see that the workers are avaliable on the monday, tuesday , wednessday, thursday,  friday , saturday and sunday. we have 7 shifts 
therefore Shift arrangement that reduce the wage cost.



